---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# futuremice

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/futuremice)](https://CRAN.R-project.org/package=futuremice)
[![Codecov test coverage](https://codecov.io/gh/jesse-smith/futuremice/branch/main/graph/badge.svg?token=tsXed2ET40)](https://codecov.io/gh/jesse-smith/futuremice)
[![R-CMD-check](https://github.com/jesse-smith/futuremice/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jesse-smith/futuremice/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`{futuremice}` parallelizes the main functionality of the `{mice}` package using
`{future}` and `{furrr}`. This enables the use of a progress bar for updates, as
well as an early stopping method to save time spent on unneeded iteration or
manual convergence checks (not quality checks - you still have to assess the
results yourself).

## Installation

You can install the development version of futuremice like so:

``` r
# You will need Rtools to install packages from Github on Windows
# `devtools` with throw an informative error if Rtools is not found
if (!"devtools" %in% installed.packages()) install.packages("devtools")
devtools::install_github("jesse-smith/futuremice")
```

## Minimal Example

Let's run the example from the `{mice}` package documentation, but in parallel.

```{r example-init}
# Load {futuremice}
library(futuremice)

# Use a local seed
withr::local_seed(1L)

# Evaluate futures in parallel - max of two workers to avoid hogging resources
future::plan("multisession", workers = pmin(2L, future::availableCores()))

# Use {progress} package for progress bar - shows diagnostics in real time
progressr::handlers("progress")
```

`{futuremice}` uses the `{future}` package to run imputations in parallel. By
default, `{future}` will run a `"sequential"` plan, which is no different
(and a little less efficient) than calling `mice::mice()`. To take advantage of
multiple CPUs, we can use a `"multisession"` plan (see the [vignette](https://future.futureverse.org/articles/future-1-overview.html#controlling-how-futures-are-resolved)
from the `{future}` package for details on different plans). `future_mice()` also
provides a progress bar and real-time convergence diagnostics using `{progressr}`;
however, the default progress bar does not show messages, so we'll use the `progress`
handler to see our diagnostics.

Now, let's impute our missing data:

```{r example-impute}
# Impute the missing values using defaults
# Use `progressr::with_progress()` to show the progress bar
mids <- progressr::with_progress(future_mice(mice::nhanes))

# Or start with `mice::mice()` and finish with `future_mids()`
mids2 <- mice::mice(mice::nhanes, maxit = 1L, printFlag = FALSE)
mids2 <- progressr::with_progress(future_mids(mids2, maxit = 100L))

# View the resulting `mids` (*m*ultiply *i*mputed *d*ata *s*et) object
mids

# List the actual imputations for BMI
mids$imp$bmi
```

Note that `future_mice()` will often run longer than `mice::mice()`'s default of
`5` imputations before convergence is confidently achieved. Also note that we
will only get a progress bar if we wrap the call in `with_progress()`; this is
a feature of the `{progressr}` package.

We can use the resulting `mids` object just like the result of a call to
`mice::mice()`. Let's inspect the quality of the imputations:

```{r example-inspect}
# Inspect quality of imputations
mice::stripplot(mids, chl, pch = 19, xlab = "Imputation number")
```

In general, we would like the imputations to be plausible, i.e., values that
could have been observed if they had not been missing. Now let's fit a model to
the imputed data set and pool the results:

```{r example-fit}
# Fit complete-data model
fit <- with(mids, lm(chl ~ age + bmi))

# Pool and summarize the results
summary(mice::pool(fit))
```

The complete-data model is fit to each imputed data set, and the results are
combined to arrive at estimates that properly account for the missing data.

We can also compare two `mids` objects using `compare_mids()`:
```{r example-compare}
compare_mids(mids, mids2, ignore_rng = TRUE)
```

This will show us where differences occur between the two objects
(if there are any). We'll ignore attributes that depend on the RNG state because
evaluating imputations in parallel requires a different kind of random number
generation than evaluating sequentially, as we did in the first iteration of
`mice::mice()`.

```{r reset-plan, include=FALSE}
future::plan("sequential")
```

## Code of Conduct

Please note that the futuremice project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
